Beam-Helicity and Beam-Charge Asymmetries \\ in the Bethe-Heitler and DVCS processes on \\ an Unpolarised Proton Target \underline{Paper Tag: PDVCS0607 (v1.3)} \underline{Drafting Committee: DC90 (\today)}

### 2011-09-07 background_and_systematic_dual.tex
Implemented Delia's and WDN's final comments and removed red text.

The contribution to the uncertainties on the amplitude measurements
arising from background in the data from neutral meson
production is \red{predominantly due to the failure to identify one of
  the two photons from the decay of produeced neutral mesons}. The procedure for estimating the corresponding
uncertainty on the measured amplitude values is described in detail in
refs.~\cite{Air08,Air09}. Each measurement in the $-t$, $x_{\textrm{B}}$ and
  $Q^{2}$ projections has this uncertainty estimated at the
  centre of the relevant kinematic bin and included as part of the
  total systematic uncertainty.

@@

The total systematic uncertainty for the 2006-2007 data sample was
determined for each kinematic bin by adding in quadrature the
  uncertainties arising from the background correction, the
  missing-mass shifts, and the detector effects.  The 1996-2005 sample also has a
systematic uncertainty from misalignment of the
spectrometer~\cite{Air09}, which has been eliminated for the 2006-2007 data sample due to improved
  surveying measurements~\cite{Bur10}. The contribution from
each uncertainty to each amplitude extracted in a single\red{, overall} kinematic bin
from the 2006-2007 data  is summarised in Table
\ref{table_systematic_contributions_0607}.

@@

\begin{table}
 \begin{center}
\resizebox{\textwidth}{!} {
 \begin{tabular}{|c|c|c|c|c|c|c|}
  \hline
 & $A$ $\pm$ $\delta_{stat.}$ $\pm$ $\delta_{syst.}$ & Background & Missing-Mass Shift  & Detector Effects & & Total \\
  \hline
  \hline
  $A_{\textrm{LU,I}}^{\sin\phi}$ & -0.222  $\pm$  0.023  $\pm$   0.022 & 0.002 & 0.001 & 0.022 & & 0.055 \\
  \hline
  $A_{\textrm{LU,DVCS}}^{\sin\phi}$ & 0.005  $\pm$  0.023  $\pm$  0.003 & 0.002 & 0.002 & 0.001 & & 0.003 \\
  \hline
  $A_{\textrm{LU,I}}^{\sin(2\phi)}$ & 0.005  $\pm$  0.023  $\pm$   0.003 & 0.003 & 0.001 & 0.001 & & 0.003 \\
  \hline
  \hline
  $A_{\textrm{C}}^{\cos(0\phi)}$ & -0.024 $\pm$  0.004 $\pm$  0.011 & 0.001 & 0.003 & 0.010 & & 0.011 \\
  \hline
  $A_{\textrm{C}}^{\cos\phi}$ & 0.032  $\pm$  0.006 $\pm$   0.002 & 0.002 & 0.001 & 0.001 & & 0.002 \\
  \hline
  $A_{\textrm{C}}^{\cos(2\phi)}$ & -0.004  $\pm$  0.005  $\pm$   0.014 & 0.001 & 0.000 & 0.014 & & 0.014 \\
  \hline
  $A_{\textrm{C}}^{\cos(3\phi)}$ & 0.001  $\pm$   0.005   $\pm$   0.004 & 0.000 & 0.001 & 0.003 & & 0.004 \\
  \hline
 \end{tabular}
}
  \caption{The contributions to the \red{overall systematic 
uncertainties of the extracted asymmetry amplitudes} due to the
background correction, the time-dependent shifts of the missing-mass
distributions and detector effects for the 2006-2007 data. The total
systematic uncertainties \red{of the amplitudes}, shown in the
right-most column, are the individual contributions added in quadrature.}
  \label{table_systematic_contributions_0607}
\end{center}
\end{table}

>>>>

The contribution to the uncertainties on the amplitude measurements
arising from background in the data from neutral meson
production is predominantly due to the failure to identify one of
  the two photons from the decay of produced neutral mesons. The procedure for estimating the corresponding
uncertainty on the measured amplitude values is described in detail in
refs.~\cite{Air08,Air09}. Each measurement in the $-t$, $x_{\textrm{B}}$ and
  $Q^{2}$ projections has this uncertainty estimated at the
  centre of the relevant kinematic bin and included as part of the
  total systematic uncertainty.

@@

The total systematic uncertainty for the 2006-2007 data sample was
determined for each kinematic bin by adding in quadrature the
  uncertainties arising from the background correction, the
  missing-mass shifts, and the detector effects.  The 1996-2005 sample also has a
systematic uncertainty from misalignment of the
spectrometer~\cite{Air09}, which has been eliminated for the 2006-2007 data sample due to improved
  surveying measurements~\cite{Bur10}. The contribution from
each uncertainty to each amplitude extracted in a single, overall kinematic bin
from the 2006-2007 data  is summarised in Table
\ref{table_systematic_contributions_0607}.

@@

\begin{table}
 \begin{center}
\resizebox{\textwidth}{!} {
 \begin{tabular}{|c|c|c|c|c|c|c|}
  \hline
 & $A$ $\pm$ $\delta_{stat.}$ $\pm$ $\delta_{syst.}$ & Background & Missing-Mass Shift  & Detector Effects & & Total \\
  \hline
  \hline
  $A_{\textrm{LU,I}}^{\sin\phi}$ & -0.222  $\pm$  0.023  $\pm$   0.022 & 0.002 & 0.001 & 0.022 & & 0.022 \\
  \hline
  $A_{\textrm{LU,DVCS}}^{\sin\phi}$ & 0.005  $\pm$  0.023  $\pm$  0.003 & 0.002 & 0.002 & 0.001 & & 0.003 \\
  \hline
  $A_{\textrm{LU,I}}^{\sin(2\phi)}$ & 0.005  $\pm$  0.023  $\pm$   0.003 & 0.003 & 0.001 & 0.001 & & 0.003 \\
  \hline
  \hline
  $A_{\textrm{C}}^{\cos(0\phi)}$ & -0.024 $\pm$  0.004 $\pm$  0.011 & 0.001 & 0.003 & 0.010 & & 0.011 \\
  \hline
  $A_{\textrm{C}}^{\cos\phi}$ & 0.032  $\pm$  0.006 $\pm$   0.002 & 0.002 & 0.001 & 0.001 & & 0.002 \\
  \hline
  $A_{\textrm{C}}^{\cos(2\phi)}$ & -0.004  $\pm$  0.005  $\pm$   0.014 & 0.001 & 0.000 & 0.014 & & 0.014 \\
  \hline
  $A_{\textrm{C}}^{\cos(3\phi)}$ & 0.001  $\pm$   0.005   $\pm$   0.004 & 0.000 & 0.001 & 0.003 & & 0.004 \\
  \hline
 \end{tabular}
}
  \caption{The contributions to the overall systematic 
uncertainties of the extracted asymmetry amplitudes due to the
background correction, the time-dependent shifts of the missing-mass
distributions and detector effects for the 2006-2007 data. The total
systematic uncertainties of the amplitudes, shown in the
right-most column, are the individual contributions added in quadrature.}
  \label{table_systematic_contributions_0607}
\end{center}
\end{table}

### 2011-09-07 experiment_and_data.tex
Implemented Delia's and WDN's final comments and removed red text.

An event sample was selected using a missing-mass technique requiring
that the squared missing-mass $M_{\textrm{X}}^{2}=(q+P-q')^{2}$
of the $e\,p \rightarrow\, e'\,\gamma\, \textrm{X}$ measurement
corresponded to the square of the proton mass within the limits of the
energy resolution of the H{\sc ermes} calorimeter. Here, $q$ is the
four-momentum of the virtual photon, $p$ is the initial four-momentum
of the target proton and $q'$ is the four-momentum of the produced
photon. The ``exclusive region'' was defined as $-$($1.5$\,GeV)$^{2} <
M_{\textrm{X}}^{2}$ $<$ (1.7\,GeV)$^{2}$, as in
ref.~\cite{Air09}. This exclusive region was shifted by up to
0.17\,GeV$^{2}$ \red{for certain subsets of the data in order }to reflect observed differences in the distributions of the electron and positron data samples~\cite{Bur10}.

@@

The asymmetry amplitudes $A_{\textrm{LU,I/DVCS}}^{\sin(n\phi)}$ and
$A_{\textrm{C}}^{\cos(n\phi)}$ relate respectively to the Fourier
coefficients $s_{n,\textrm{unp}}^{W}$ and $c_{n,\textrm{unp}}^{I}$ from the interference and
DVCS terms in Eqs.~\ref{e:alui}-\ref{e:ac}. The asymmetry amplitudes
may also be affected by the lepton propagators and the other
$\phi$-dependent terms in the denominators in
Eqs.~\ref{e:alui}-\ref{e:ac}. The  $s_{n,\textrm{unp}}^{W}$ and $c_{n,\textrm{unp}}^{V}$ Fourier
coefficients depend on ``$\mathcal{C}$-functions'' \cite{{Bel02b}}, each of which is a
combination of complex Compton Form Factors (CFF\red{s}). A CFF is a convolution of a GPD with a hard scattering kernel. Contributions of GPDs to the cross section may be relatively suppressed by powers of $1/Q$, the origin of which may be kinematic in nature or due to the twist level of the GPD. Leading twist is twist-2. Typically, the contribution of a twist-$n$ GPD, and hence the corresponding CFF, is suppressed by $\mathcal{O}(1/Q^{n-2})$. Table~\ref{tab_amplitudes} presents the asymmetry amplitudes extracted in this analysis and the related Fourier coefficients, dominant $\mathcal{C}$-function, twist-level and level of suppression.

At H{\sc ermes} kinematic conditions, the leading-twist beam-helicity asymmetry amplitude is $A_{\textrm{LU,I}}^{\sin\phi}$ and the leading beam-charge asymmetry amplitude is $A^{\cos\phi}_{\textrm{C}}$. These asymmetry amplitudes, for an unpolarised target, are sensitive respectively to Fourier coefficients $s_{1,\textrm{unp}}^{\textrm{I}}$ and $c_{1,\textrm{unp}}^{\textrm{I}}$. Both of these Fourier coefficients have a dominant contribution from the $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function:
\begin{eqnarray}
s_{1,\textrm{unp}}^{\textrm{I}} \approx&\,\,\,\,8\lambda ky(2-y)\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}\quad\red{\textrm{and}}&\label{eq:s1}
\\
 c_{1,\textrm{unp}}^{\textrm{I}} \approx&8k(2- 2y + y^{2})\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}\,,&\label{eq:c1}
\end{eqnarray}
where the definition of the kinematic factor $k$ is found
  in ref.\cite{Bel02b}. The $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function can be
written
\cite{Bel02b} 
\begin{equation}
 \mathcal{C}_{\textrm{unp}}^{\textrm{I}} = F_{1}\mathcal{H} + \frac{x_{\textrm{B}}}{2-x_{\textrm{B}}}(F_{1}+F_{2})\widetilde{\mathcal{H}} -\frac{t}{4M^{2}}F_{2}\mathcal{E},
\label{Eq_cunp}
\end{equation}
where $F_{1}$ and $F_{2}$ are respectively the Dirac and Pauli form
factors of the nucleon and $\mathcal{H}$, $\widetilde{\mathcal{H}}$ and
$\mathcal{E}$ are CFFs that relate respectively to the GPDs $H$,
$\widetilde{H}$ and $E$.  At H{\sc ermes} kinematic
conditions (where $x_{\textrm{B}}$ and $\frac{-t}{4M^2}$ are of order 0.1), the
contributions of CFFs $\widetilde{\mathcal{H}}$ and $\mathcal{E}$ can be
neglected in Eq.~\ref{Eq_cunp} (in first approximation) with respect to $\mathcal{H}$ since they
are kinematically suppressed by an order of magnitude or more.
Hence, the behaviour of
$\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ is determined by CFF $\mathcal{H}$
and therefore GPD $H$ can be constrained through
measurements of $A_{\textrm{LU,I}}^{\sin\phi}$ and $A^{\cos\phi}_{\textrm{C}}$.
The asymmetry amplitudes $A_{\textrm{LU},\textrm{I}}^{\sin(2\phi)}$,
$A^{\cos(0\phi)}_{\textrm{C}}$ and $A^{\cos(2\phi)}_{\textrm{C}}$ also depend
upon this $\mathcal{C}$-function. However, the $A^{\cos(0\phi)}_{\textrm{C}}$ amplitude is kinematically suppressed compared to the $A^{\cos\phi}_{\textrm{C}}$ amplitude, and the  $A_{\textrm{LU,I}}^{\sin(2\phi)}$ and $A^{\cos(2\phi)}_{\textrm{C}}$ amplitudes are higher\red{-}twist quantities (see Table~\ref{tab_amplitudes}).

The DVCS asymmetry amplitude $A^{\sin\phi}_{\textrm{LU,DVCS}}$ has a
contribution from the $\mathcal{C}_{\textrm{unp}}^{\textrm{DVCS}}$\red{-}function,
which is bilinear in CFFs. However, this twist-3 amplitude is inherently small at HERMES kinematic conditions due to the size of the $s_{1}^{\textrm{DVCS}}$ Fourier coefficient compared to the contribution from the $c_{n}^{\textrm{BH}}$ coefficients in the denominator of Eq.~\ref{e:aludvcs}. As a result of
the more complicated dependence on the CFFs and this suppression, it
is more difficult to constrain GPDs
via the measurement of $A^{\sin\phi}_{\textrm{LU,DVCS}}$ than from the
kinematically-unsuppressed leading-twist amplitudes.

The $A^{\cos(3\phi)}_{\textrm{C}}$ amplitude depends on the
$c_{3,\textrm{unp}}^{\textrm{I}}$ Fourier coefficient and hence the
$\mathcal{C}_{\textrm{T,unp}}^{\textrm{I}}$\red{-}function. Although the CFFs
in this function are of leading twist, they relate to gluon helicity-flip GPDs and are thus suppressed by $\alpha_{\textrm{S}}/\pi$,
where $\alpha_{\textrm{S}}$ is the strong coupling constant.
\begin{table}
\begin{center}
\resizebox{\textwidth}{!} {
\begin{tabular}{|c|c|c|c|c|}
\hline
Asymmetry Amplitude& Fourier Coefficient& Dominant CFF Dependence & Twist Level & Relative Suppression   \\ 
\hline
\hline
$A_{\textrm{LU,I}}^{\sin\phi}$ & $s_{1,\textrm{unp}}^{\textrm{I}}$  &
$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$
&  2 & --\\
\hline
$A_{\textrm{LU,I}}^{\sin(2\phi)}$ & $s_{2,\textrm{unp}}^{\textrm{I}}$ 
&
$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$
&  3 & $1/Q$\\
\hline
\hline
$A_{\textrm{LU,DVCS}}^{\sin\phi}$ & $s_{1, \textrm{unp}}^{\textrm{DVCS}}$ &
$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{DVCS}}$ &  3 & $1/Q$ \\
\hline
\hline
$A_{\textrm{C}}^{\cos(0\phi)}$ & $c_{0,\textrm{unp}}^{\textrm{I}}$  &
$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2& $\frac{(2-y)^2K}{(1-y)(2-2y+y^2)}$
\\
\hline
$A_{\textrm{C}}^{\cos\phi}$ & $c_{1,\textrm{unp}}^{\textrm{I}}$  &
$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2 & --
\\
\hline
$A_{\textrm{C}}^{\cos(2\phi)}$ & $c_{2,\textrm{unp}}^{\textrm{I}}$ &
$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 3 & $1/Q$ \\
\hline
$A_{\textrm{C}}^{\cos(3\phi)}$ & $c_{3,\textrm{unp}}^{\textrm{I}}$ &
$\mathfrak{Re}\mathcal{C}_{\textrm{T,unp}}^{\textrm{I}}$ &  2 & $\alpha_{\textrm{S}}/\pi$ \\
\hline
 \end{tabular}
}
\caption{Asymmetry amplitudes that can
be extracted from the available data set, the related Fourier
coefficients, dominant $\mathcal{C}$-function, twist-level and level of
suppression relative to the leading amplitudes at H{\sc ermes} kinematic conditions. {The constant K is defined in ref.~\cite{Bel02b}}.}
\label{tab_amplitudes}
\end{center}
\end{table}

>>>>

An event sample was selected using a missing-mass technique requiring
that the squared missing-mass $M_{\textrm{X}}^{2}=(q+P-q')^{2}$
of the $e\,p \rightarrow\, e'\,\gamma\, \textrm{X}$ measurement
corresponded to the square of the proton mass within the limits of the
energy resolution of the H{\sc ermes} calorimeter. Here, $q$ is the
four-momentum of the virtual photon, $p$ is the initial four-momentum
of the target proton and $q'$ is the four-momentum of the produced
photon. The ``exclusive region'' was defined as $-$($1.5$\,GeV)$^{2} <
M_{\textrm{X}}^{2}$ $<$ (1.7\,GeV)$^{2}$, as in
ref.~\cite{Air09}. This exclusive region was shifted by up to
0.17\,GeV$^{2}$ for certain subsets of the data in order to reflect observed differences in the distributions of the electron and positron data samples~\cite{Bur10}.

@@

The asymmetry amplitudes $A_{\textrm{LU,I/DVCS}}^{\sin(n\phi)}$ and
$A_{\textrm{C}}^{\cos(n\phi)}$ relate respectively to the Fourier
coefficients $s_{n,\textrm{unp}}^{W}$ and $c_{n,\textrm{unp}}^{I}$ from the interference and
DVCS terms in Eqs.~\ref{e:alui}-\ref{e:ac}. The asymmetry amplitudes
may also be affected by the lepton propagators and the other
$\phi$-dependent terms in the denominators in
Eqs.~\ref{e:alui}-\ref{e:ac}. The  $s_{n,\textrm{unp}}^{W}$ and $c_{n,\textrm{unp}}^{V}$ Fourier
coefficients depend on ``$\mathcal{C}$-functions'' \cite{{Bel02b}}, each of which is a
combination of complex Compton Form Factors (CFFs). A CFF is a
convolution of a GPD with a hard scattering kernel. Contributions of
GPDs to the cross section may be relatively suppressed by powers of
$1/Q$, the origin of which may be kinematic in nature or due to the
twist level of the GPD. Leading twist is twist-2. Typically, the
contribution of a twist-$n$ GPD, and hence the corresponding CFF, is
suppressed by $\mathcal{O}(1/Q^{n-2})$. Table~\ref{tab_amplitudes}
presents the asymmetry amplitudes extracted in this analysis and the
related Fourier coefficients, dominant $\mathcal{C}$-function, twist-level and level of suppression.

At H{\sc ermes} kinematic conditions, the leading-twist beam-helicity asymmetry amplitude is $A_{\textrm{LU,I}}^{\sin\phi}$ and the leading beam-charge asymmetry amplitude is $A^{\cos\phi}_{\textrm{C}}$. These asymmetry amplitudes, for an unpolarised target, are sensitive respectively to Fourier coefficients $s_{1,\textrm{unp}}^{\textrm{I}}$ and $c_{1,\textrm{unp}}^{\textrm{I}}$. Both of these Fourier coefficients have a dominant contribution from the $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function:
\begin{eqnarray}
s_{1,\textrm{unp}}^{\textrm{I}} \approx&\,\,\,\,8\lambda ky(2-y)\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}\quad\textrm{and}&\label{eq:s1}
\\
 c_{1,\textrm{unp}}^{\textrm{I}} \approx&8k(2- 2y + y^{2})\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}\,,&\label{eq:c1}
\end{eqnarray}
where the definition of the kinematic factor $k$ is found
  in ref.\cite{Bel02b}. The $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function can be
written
\cite{Bel02b} 
\begin{equation}
 \mathcal{C}_{\textrm{unp}}^{\textrm{I}} = F_{1}\mathcal{H} + \frac{x_{\textrm{B}}}{2-x_{\textrm{B}}}(F_{1}+F_{2})\widetilde{\mathcal{H}} -\frac{t}{4M^{2}}F_{2}\mathcal{E},
\label{Eq_cunp}
\end{equation}
where $F_{1}$ and $F_{2}$ are respectively the Dirac and Pauli form
factors of the nucleon and $\mathcal{H}$, $\widetilde{\mathcal{H}}$ and
$\mathcal{E}$ are CFFs that relate respectively to the GPDs $H$,
$\widetilde{H}$ and $E$.  At H{\sc ermes} kinematic
conditions (where $x_{\textrm{B}}$ and $\frac{-t}{4M^2}$ are of order 0.1), the
contributions of CFFs $\widetilde{\mathcal{H}}$ and $\mathcal{E}$ can be
neglected in Eq.~\ref{Eq_cunp} (in first approximation) with respect to $\mathcal{H}$ since they
are kinematically suppressed by an order of magnitude or more.
Hence, the behaviour of
$\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ is determined by CFF $\mathcal{H}$
and therefore GPD $H$ can be constrained through
measurements of $A_{\textrm{LU,I}}^{\sin\phi}$ and $A^{\cos\phi}_{\textrm{C}}$.
The asymmetry amplitudes $A_{\textrm{LU},\textrm{I}}^{\sin(2\phi)}$,
$A^{\cos(0\phi)}_{\textrm{C}}$ and $A^{\cos(2\phi)}_{\textrm{C}}$ also depend
upon this $\mathcal{C}$-function. However, the $A^{\cos(0\phi)}_{\textrm{C}}$ amplitude is kinematically suppressed compared to the $A^{\cos\phi}_{\textrm{C}}$ amplitude, and the  $A_{\textrm{LU,I}}^{\sin(2\phi)}$ and $A^{\cos(2\phi)}_{\textrm{C}}$ amplitudes are higher-twist quantities (see Table~\ref{tab_amplitudes}).

The DVCS asymmetry amplitude $A^{\sin\phi}_{\textrm{LU,DVCS}}$ has a
contribution from the $\mathcal{C}_{\textrm{unp}}^{\textrm{DVCS}}$-function,
which is bilinear in CFFs. However, this twist-3 amplitude is inherently small at HERMES kinematic conditions due to the size of the $s_{1}^{\textrm{DVCS}}$ Fourier coefficient compared to the contribution from the $c_{n}^{\textrm{BH}}$ coefficients in the denominator of Eq.~\ref{e:aludvcs}. As a result of
the more complicated dependence on the CFFs and this suppression, it
is more difficult to constrain GPDs
via the measurement of $A^{\sin\phi}_{\textrm{LU,DVCS}}$ than from the
kinematically-unsuppressed leading-twist amplitudes.

The $A^{\cos(3\phi)}_{\textrm{C}}$ amplitude depends on the
$c_{3,\textrm{unp}}^{\textrm{I}}$ Fourier coefficient and hence the
$\mathcal{C}_{\textrm{T,unp}}^{\textrm{I}}$-function. Although the CFFs
in this function are of leading twist, they relate to gluon helicity-flip GPDs and are thus suppressed by $\alpha_{\textrm{S}}/\pi$,
where $\alpha_{\textrm{S}}$ is the strong coupling constant.
\begin{table}
\begin{center}
\resizebox{\textwidth}{!} {
\begin{tabular}{|c|c|c|c|c|}
\hline
Asymmetry Amplitude& Fourier Coefficient& Dominant CFF Dependence & Twist-Level & Relative Suppression   \\ 
\hline
\hline
$A_{\textrm{LU,I}}^{\sin\phi}$ & $s_{1,\textrm{unp}}^{\textrm{I}}$  &
$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$
&  2 & --\\
\hline
$A_{\textrm{LU,I}}^{\sin(2\phi)}$ & $s_{2,\textrm{unp}}^{\textrm{I}}$ 
&
$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$
&  3 & $1/Q$\\
\hline
\hline
$A_{\textrm{LU,DVCS}}^{\sin\phi}$ & $s_{1, \textrm{unp}}^{\textrm{DVCS}}$ &
$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{DVCS}}$ &  3 & $1/Q$ \\
\hline
\hline
$A_{\textrm{C}}^{\cos(0\phi)}$ & $c_{0,\textrm{unp}}^{\textrm{I}}$  &
$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2& $\frac{(2-y)^2K}{(1-y)(2-2y+y^2)}$
\\
\hline
$A_{\textrm{C}}^{\cos\phi}$ & $c_{1,\textrm{unp}}^{\textrm{I}}$  &
$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2 & --
\\
\hline
$A_{\textrm{C}}^{\cos(2\phi)}$ & $c_{2,\textrm{unp}}^{\textrm{I}}$ &
$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 3 & $1/Q$ \\
\hline
$A_{\textrm{C}}^{\cos(3\phi)}$ & $c_{3,\textrm{unp}}^{\textrm{I}}$ &
$\mathfrak{Re}\mathcal{C}_{\textrm{T,unp}}^{\textrm{I}}$ &  2 & $\alpha_{\textrm{S}}/\pi$ \\
\hline
 \end{tabular}
}
\caption{Asymmetry amplitudes that can
be extracted from the available data set, the related Fourier
coefficients, dominant $\mathcal{C}$-function, twist-level and level of
suppression relative to the leading amplitudes at H{\sc ermes} kinematic conditions. {The constant K is defined in ref.~\cite{Bel02b}}.}
\label{tab_amplitudes}
\end{center}
\end{table}

### 2011-09-07 results_dual.tex
Implemented Delia's and WDN's final comments and removed red text.

The results of the beam-helicity and beam-charge asymmetry amplitudes extracted from the complete 1996-2007 hydrogen sample are shown in Figs.~\ref{bsa_xbjrange} and \ref{bca_xbjrange}. The number of analysable events available from the 2006-2007 data set (70352) is approximately three times greater than the number of events recorded in the 1996-2005 sample (24817). The  asymmetry amplitudes extracted from the complete 1996-2007 data set thus resemble the 2006-2007 result. This resemblance is not so evident for the beam-helicity asymmetry amplitudes because the beam polarisation was lower in 2006 and 2007 than in 1996-2005, giving the 2006\red{-}2007 data a lower weighting in the combined fit.

The first and second harmonics of $\mathcal{A}_{\textrm{LU,I}}$, which are
sensitive to the interference term in the scattering amplitude, are shown in the first and third rows of Fig.~\ref{bsa_xbjrange}. The leading-twist amplitude $A_{\textrm{LU,I}}^{\sin\phi}$ has the largest magnitude of any of the amplitudes when extracted in a single bin from the entire data set. This amplitude shows no strong dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$, implying a strong dependence at smaller values of $-t$ as the amplitude must approach zero as $-t$ approaches zero due to the dependence of the amplitude on the factor $k$ from Eq.~\ref{eq:s1}. The $A_{\textrm{LU,I}}^{\sin\phi}$ amplitude is sensitive to the imaginary part of the CFF $\mathcal{H}$ and thereby can constrain GPD $\textit{H}$. The $A_{\textrm{LU,DVCS}}^{\sin\phi}$ asymmetry is shown in the second row of Fig.~\ref{bsa_xbjrange}. Both the $A_{\textrm{LU,DVCS}}^{\sin\phi}$ asymmetry amplitude and the $A_{\textrm{LU,I}}^{\sin(2\phi)}$ asymmetry amplitude are compatible with zero, and neither asymmetry amplitude shows any dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$. The systematic error bands associated with the asymmetry amplitudes extracted from the combined data set were determined using Monte Carlo simulations as explained in section~4. The missing-mass uncertainty for the combined data set was calculated using the procedure described in that section and the results were added in quadrature.

The $A_{\textrm{C}}^{\cos(n\phi)}$ amplitudes are shown in Fig.~\ref{bca_xbjrange}. The systematic uncertainties are estimated in the same procedure as \red{used to estimate the systematic uncertainties of} the beam-helicity asymmetries. The leading-twist $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ amplitudes are both non-zero. There is an expected relationship between $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ as the Fourier coefficient $c^{\textrm{I}}_{0,\textrm{unp}}$ is inversely proportional to $c^{\textrm{I}}_{1,\textrm{unp}}$ via the kinematic factor $k$ from Eq.~\ref{eq:c1}. These amplitudes are found to diverge with opposite sign from zero at increasing values of $-t$ but they
have no discernible dependence on $x_{\textrm{B}}$ and $Q^{2}$. The $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ amplitudes are both consistent with zero and have no significant variation in value over the range in $-t$, $x_{\textrm{B}}$ and $Q^{2}$. The $A_{C}^{\cos(2\phi)}$ amplitude is related to twist-3 GPDs and $A_{\textrm{C}}^{\cos(3\phi)}$ relates to gluon helicity-flip GPDs. Both of these amplitudes are expected to be suppressed at H{\sc ermes} kinematic conditions compared to the leading-twist amplitudes.

@@

In order to provide more detailed information that can be used in future fits, in particular for the determination of the entanglement of the skewness and $-t$ dependences of GPDs, the amplitudes already presented in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} are shown as a function of $-t$ for three different ranges of $x_{\textrm{B}}$ in Figs.~\ref{bsa_xbjrange2} and~\ref{bca_xbjrange2}. \red{These figures represent the kinematic dependences of the amplitudes in a less-correlated manner than the one dimensional projections}. There is no observed $-t$ dependence of any of the $\mathcal{A}_{\textrm{LU}}$ amplitudes in any of the distinct ranges of $x_{\textrm{B}}$. No additional features or $-t$ dependences are observed for the $\mathcal{A}_{\textrm{C}}$ amplitudes in these separate $x_{\textrm{B}}$ ranges.

>>>>

The results of the beam-helicity and beam-charge asymmetry amplitudes extracted from the complete 1996-2007 hydrogen sample are shown in Figs.~\ref{bsa_xbjrange} and \ref{bca_xbjrange}. The number of analysable events available from the 2006-2007 data set (70352) is approximately three times greater than the number of events recorded in the 1996-2005 sample (24817). The  asymmetry amplitudes extracted from the complete 1996-2007 data set thus resemble the 2006-2007 result. This resemblance is not so evident for the beam-helicity asymmetry amplitudes because the beam polarisation was lower in 2006 and 2007 than in 1996-2005, giving the 2006\red{-}2007 data a lower weighting in the combined fit. The systematic error bands associated with the asymmetry amplitudes extracted from the combined data set were determined using Monte Carlo simulations as explained in section~4. The missing-mass uncertainty for the combined data set was calculated using the procedure described in that section and the results were added in quadrature.

The first and second harmonics of $\mathcal{A}_{\textrm{LU,I}}$, which are
sensitive to the interference term in the scattering amplitude, are shown in the first and third rows of Fig.~\ref{bsa_xbjrange}. The leading-twist amplitude $A_{\textrm{LU,I}}^{\sin\phi}$ has the largest magnitude of any of the amplitudes when extracted in a single bin from the entire data set. This amplitude shows no strong dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$, implying a strong dependence at smaller values of $-t$ as the amplitude must approach zero as $-t$ approaches zero due to the dependence of the amplitude on the factor $k$ from Eq.~\ref{eq:s1}. The $A_{\textrm{LU,I}}^{\sin\phi}$ amplitude is sensitive to the imaginary part of the CFF $\mathcal{H}$ and thereby can constrain GPD $\textit{H}$. The $A_{\textrm{LU,DVCS}}^{\sin\phi}$ asymmetry is shown in the second row of Fig.~\ref{bsa_xbjrange}. Both the $A_{\textrm{LU,DVCS}}^{\sin\phi}$ asymmetry amplitude and the $A_{\textrm{LU,I}}^{\sin(2\phi)}$ asymmetry amplitude are compatible with zero, and neither asymmetry amplitude shows any dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$.

The $A_{\textrm{C}}^{\cos(n\phi)}$ amplitudes are shown in Fig.~\ref{bca_xbjrange}. The systematic uncertainties are estimated in the same procedure as used to estimate the systematic uncertainties of the beam-helicity asymmetries. The leading-twist $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ amplitudes are both non-zero. There is an expected relationship between $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ as the Fourier coefficient $c^{\textrm{I}}_{0,\textrm{unp}}$ is inversely proportional to $c^{\textrm{I}}_{1,\textrm{unp}}$ via the kinematic factor $k$ from Eq.~\ref{eq:c1}. These amplitudes are found to diverge with opposite sign from zero at increasing values of $-t$ but they
have no discernible dependence on $x_{\textrm{B}}$ and $Q^{2}$. The $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ amplitudes are both consistent with zero and have no significant variation in value over the range in $-t$, $x_{\textrm{B}}$ and $Q^{2}$. The $A_{C}^{\cos(2\phi)}$ amplitude is related to twist-3 GPDs and $A_{\textrm{C}}^{\cos(3\phi)}$ relates to gluon helicity-flip GPDs. Both of these amplitudes are expected to be suppressed at H{\sc ermes} kinematic conditions compared to the leading-twist amplitudes.

@@

In order to provide more detailed information that can be used in future fits, in particular for the determination of the entanglement of the skewness and $-t$ dependences of GPDs, the amplitudes already presented in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} are shown as a function of $-t$ for three different ranges of $x_{\textrm{B}}$ in Figs.~\ref{bsa_xbjrange2} and~\ref{bca_xbjrange2}. These figures represent the kinematic dependences of the amplitudes in a less-correlated manner than the one dimensional projections. There is no observed $-t$ dependence of any of the $\mathcal{A}_{\textrm{LU}}$ amplitudes in any of the distinct ranges of $x_{\textrm{B}}$. No additional features or $-t$ dependences are observed for the $\mathcal{A}_{\textrm{C}}$ amplitudes in these separate $x_{\textrm{B}}$ ranges.
